\chapter{Materials Used in First Focus Group}
\label{app:first_group}
The following materials were used to provide context and information during the first focus group session, as well as before the session as pre-tasking material. Unless noted otherwise, the materials are provided in this chapter.

\begin{itemize}
	\item Description of CRM systems and functionality
	\item Screen shots of CRM systems (see appendix~\ref{app:screenshots})
	\item Existing heuristics identified in literature review (see appendix~\ref{appsec:litrev_list})
		\begin{itemize}
			\item Heuristics developed by \citet{Nielsen1994a}
			\item Heuristics for ERP systems developed by \citet{Singh2009}
			\item Heuristics for e-learning systems developed by \citet{Ardito2006}
		\end{itemize}
	\item Online live demo of Microsoft Dynamics CRM and salesforce.com
\end{itemize}

\section{Recruitment Material}
\input{./recruitment/expert}

\section{Background Questionnaire}
The following questions were used to collect information about the participants' experience in fields relevant to the study. The answers were collected through paper forms and were linked to the participants' responses throughout the study by assigning a unique ID number to each participant.

\tabulinesep=_2mm^2mm
\begin{longtabu} to \textwidth {X[1, p] r}		
	How many years of experience do you have working in the usability field? & \underline{\makebox[1in]{}}\\	
	How many years of experience do you have evaluating, designing, or developing user interfaces? & \underline{\makebox[1in]{}}\\
	How many years of experience do you have using a CRM system? & \underline{\makebox[1in]{}}\\	
	How many years of experience do you have evaluating, designing, or developing CRM systems? & \underline{\makebox[1in]{}}
\end{longtabu}

\section{Description of CRM Systems}
Customer relationship management (CRM) systems are used by many organizations to implement targeted marketing and advertising strategies and to build lucrative relationships with customers. To this end, these systems offer certain common functionalities \citep{Chaffey2011,Band2010b}:

\begin{itemize}
	\item Customer selection (identify types of customers to target, segment customers): customer business intelligence, customer data management
	\item Customer acquisition (perform marketing activities to form relationships with new customers): sales force automation (leads management, approval workflows, quoting), revenue and pricing management, order management
	\item Customer retention (perform marketing activities to maintain relationships with customers): electronic bill presentment and payment, interactive voice response, contact center infrastructure, customer service and support
	\item Customer extension (increase depth or range of products a customer purchases from the company): sales force automation, customer service management
\end{itemize}

\section{Instructions for Participants}
\subsection{Setup for Group Support System}
\begin{itemize}
\item URL: [removed]
\item User Name: [removed]
\item Session ID: [removed]
\item Session Passkey: [removed]
\end{itemize}

\subsection{Tasks}
\subsubsection*{Step 1}
Please review the informational materials about CRM systems on your desk. These materials include a short description of CRM systems and typical functionality and screen shots of two different web-based CRM systems. In addition, there should be a browser window open on your computer. The browser is logged into two web-based CRM systems (Microsoft Dynamics CRM and salesforce.com) you can interact with to familiarize yourself with their functionality.

\subsubsection*{Step 2}
Please review the list of heuristics on your desk. By design, some of these heuristics may be more applicable to web-based CRM systems than others. There may be some heuristics which seem like duplicates or are very similar to each other, but this is also intentional.

Log on to the group support system using the information provided above, where you will find the same list of usability heuristics. Please cast your vote with regard to how applicable you think each individual heuristic is to web-based CRM systems. You can also indicate whether you think any modifications to the original wording are necessary to account for CRM systems.

\subsubsection*{Step 3}
Once you are done voting, please proceed to the brainstorming activity. Please enter any heuristics that you think are relevant to web-based CRM systems, but are not present in the list you reviewed during the previous activity. As other participants enter their ideas, you can comment on them.

\subsubsection*{Step 4}
Participate in the group discussion led by the moderator.

\subsubsection*{Step 5}
Fill out the short questionnaire about your professional background.
